---
title: "visual_markdown"
author: '10859333'
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# **Hello world**
## *Let's do visualisation*
This is my assignment,first I will load my packages
```{r,message = FALSE}
library(tidyverse)
```

Then I use the mpg dataset (which is a dataset that contains information about cars) to build a visualisation that plots the points corresponding to city fuel economy (cty) on the y-axis and manufacturer on the x-axis.
```{r,message = FALSE}
mpg %>%
  ggplot(aes(x = manufacturer,y = cty)) + 
  geom_point()
```

To make the x-axis labels more easy to read, use the str_to_title() function to change the manufacturer labels to title case, and adjust the axis labels easily using the theme() function. 
```{r}
mpg %>%
  mutate(manufacturer = str_to_title(manufacturer)) %>%
  ggplot(aes(x = manufacturer, y =cty)) +
  geom_point() +
  theme(axis.text.x = element_text(angle=45,vjust=0.5,hjust= .5))
```

To jitter the points, using the geom_jitter() function, and tidy up the axis titles using the labs() function to explicitly add axis labels 
```{r}
mpg %>%
  mutate(manufacturer = str_to_title(manufacturer)) %>%
  ggplot(aes(x = manufacturer, y =cty)) +
  geom_jitter(width = .2,alpha= .75, size=2)+
  theme_minimal()+
  theme(axis.text.x=element_text(angle=45,vjust=0.5,hjust= .5))+
  theme(text=element_text(size=13))+
  labs(title="City Fuel Economy by CAr Manufaturer",
       x="Manufacturer",
       y="City Fuel Economy(mpg)")
```

# ***Here is the end, have a nice day!***